Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-06 prop_letter.tex
prop_letter.tex \section{Born} Updating...

Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
postulates of the quantum probability measures first, and then introduce
the Born rule which induces the quantum probability measures for each
state. When we shift our attention to QIVPMs, we also want to construct
a QIVPMs according to a simple rule. Since the ranges of the quantum
probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
respectively, if there is a function~$\iota$ mapping any number~$x\in\left[0,1\right]$
to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
and get a QIVPM~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
Although the idea is simple, $\iota$ needs to satisfy some conditions;
otherwise, the concatenated function~$\bar{\mu}$ may not be a QIVPM.

@@

If the first three constraints, Eqs.~(\ref{eq:iota-constraints}),
fails, it is easy to see that the concatenated function~$\iota\circ\mu$
may not be a QIVPM. Suppose $\iota$ fails to satisfy Eq.~(\ref{eq:iota-Inclusion}),
consider the state
\begin{equation}
\begin{aligned}\rho= & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
 & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
\end{aligned}
\end{equation}
Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
Then,
\begin{equation}
\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
\nsubseteq & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\\
= & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\end{aligned}
\end{equation}
Therefore, $\iota$ must satisfy Eqs.~(\ref{eq:iota-constraints})
and Eq.~(\ref{eq:iota-Inclusion}) to guarantee $\iota\circ\mu$
is always a QIVPM.

>>>>

\yutsung{Notice that the use of quantum is minumalized in this section.
In another word, the results of this section should apply to both
quantum and classical case.}

Recall in Sec.~\ref{sec:fuzzy}, we illustrate the non-constructive
postulates of the quantum probability measures first, and then introduce
the Born rule which induces the quantum probability measures for each
state. When we shift our attention to QIVPMs, we also want to construct
a QIVPMs according to a simple rule. Since the ranges of the quantum
probability measures and QIVPMs are $\left[0,1\right]$ and $\mathscr{I}$,
respectively, if there is a function~$\iota$ mapping a number~$x\in\left[0,1\right]$
to $\iota\left(x\right)\in\mathscr{I}$, then we can concatenate it
with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
and get a QIVPM~$\bar{\mu}:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
Although their concatenation $\iota\circ\mu$ is always a function
from $\events$ to $\mathscr{I}$, to guarantee $\iota\circ\mu$ is
a QIVPM, $\iota$ needs to satisfy some extra conditions.

@@

If $\iota$ fails to satisfy the first three constraints, Eqs.~(\ref{eq:iota-constraints}),
it is easy to see that the concatenated function~$\iota\circ\mu$
may not be a QIVPM. Suppose $\iota$ fails to satisfy Eq.~(\ref{eq:iota-Inclusion}),
consider the state
\begin{equation}
\begin{aligned}\rho= & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
 & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
\end{aligned}
\end{equation}
Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
Then,
\begin{equation}
\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
\nsubseteq & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\\
= & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\end{aligned}
\end{equation}
Therefore, $\iota$ must satisfy Eqs.~(\ref{eq:iota-constraints})
and Eq.~(\ref{eq:iota-Inclusion}) to guarantee $\iota\circ\mu$
is always a QIVPM.
